Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-02-28 papers/CADE19/paper.tex
tidy

\documentclass{llncs}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{todonotes}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Optimising Age/Weight Ratios} \label{sec:awr:study}

@@

\subsection{Experiments}
As an initial illustrative example of how varying the AWR effects the number of clauses required to be processed before a proof is found consider Figure \ref{fig:example-optimal-awr}. This shows \todo{FINISH}

  shows the effect of varying AWR on an illustrative problem from TPTP: a smaller number of activations means that fewer clauses were processed, which in general means that a proof was found faster\footnote{
It should be noted that if a small number of clauses are extremely expensive to process it may be slower than a larger number of less-expensive clauses, but in general this is a good heuristic measure for prover performance.
It also avoids reproducibility issues involved with using system timing approaches.
}.
On this problem, a good AWR value is over 400\% better by this metric than the worst AWR value.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.8\textwidth]{example-optimal-awr}
	\caption{
The number of activations reported by Vampire after successful 1-second runs on a TPTP problem.
In between the peaks on either side, the function of \(L\) is discontinuous with large peaks and troughs, but does follow an approximate trend and settles toward the global optimum.
These properties are typical for the observed set of problems.
}
	\label{fig:example-optimal-awr}
\end{figure}

This experiment was repeated on the whole TPTP problem set, excluding problems Vampire does not support, problems which were not solved by the default mode in under a second for any AWR value, and problems solved in pre-processing.
The whole set yielded similar AWR data for 7,947 problems.
These data show that while there is no ``best'' AWR for the whole set (Table \ref{tab:no-best-awr}), choosing a good AWR value for a problem is well-rewarded (Table \ref{tab:awr-improvement}).

\todo{This discussion should be expanded. Results need more explanation and we should summarise e.g. yes we confirmed assumptions.}

@@

\begin{figure}
	\subfloat{\includegraphics[width=0.5\textwidth]{shape-decay}}
	\subfloat{\includegraphics[width=0.5\textwidth]{shape-converge}}
	\caption{The new \emph{decay} and \emph{converge} AWR shapes as implemented in Vampire. Different curves exhibit the effect of the AWR shape frequency setting.}
	\label{fig:decay-and-converge}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}
\label{sec:experiments}
\todo{Only mention CASC once and refer to portfolio mode elsewhere.}
An experimental evaluation of this approach on the TPTP\footnote{version 7.1.0} benchmark~\cite{tptp} follows.
Vampire first ran to establish baseline performance in its competition \emph{CASC mode} on all problems in TPTP, with a wallclock time limit of 300 seconds.
For experimental purposes, the same environment was preserved with the exception of activating the new ``shapes'' settings with a range of different shape frequencies.

@@

>>>>

\documentclass{llncs}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{todonotes}
%\newcommand{\todo}[1]{}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Optimising Age/Weight Ratios} \label{sec:awr:study}

@@

\subsection{Experiments}
As an initial illustrative example of how varying the AWR effects the number of clauses required to be processed before a proof is found consider Figure \ref{fig:example-optimal-awr}. This demonstrates the effect that varying AWR can have: a smaller number of activations means that fewer clauses were processed, which in general means that a proof was found faster\footnote{
It should be noted that if a small number of clauses are extremely expensive to process it may be slower than a larger number of less-expensive clauses, but in general this is a good heuristic measure for prover performance.
It also avoids reproducibility issues involved with using system timing approaches.
}.
On this problem, a good AWR value is over 400\% better by this metric than the worst AWR value.

This experiment was repeated on the whole TPTP problem set, excluding problems Vampire does not support, problems which were not solved by the default mode in under a second for any AWR value, and problems solved in pre-processing. The whole set yielded similar AWR data for 7,947 problems. 
%
We selected a sensible set of AWR values (see Table \ref{tab:awr-improvement}) - these are the values used in Vampire's portfolio mode. These tend to favour weight-first over age-first as this has been experimentally shown to be preferable.

The results of these experiments are presented in Tables \ref{tab:no-best-awr} and \ref{tab:awr-improvement}. 
%
Table \ref{tab:no-best-awr}  shows that there is no ``best'' AWR for the whole set. 
%
Table \ref{tab:awr-improvement} shows that choosing a good AWR value for a problem is well-rewarded. 
%
Therefore, these experimental results confirm the previous assumptions often made in folklore.

@@

\begin{figure}[t]
	\subfloat{\includegraphics[width=0.5\textwidth]{shape-decay}}
	\subfloat{\includegraphics[width=0.5\textwidth]{shape-converge}}
	\caption{The new \emph{decay} and \emph{converge} AWR shapes as implemented in Vampire. Different curves exhibit the effect of the AWR shape frequency setting.}
	\label{fig:decay-and-converge}
\end{figure}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}
\label{sec:experiments}
\todo{Only mention CASC once and refer to portfolio mode elsewhere.}
An experimental evaluation of this approach on the TPTP\footnote{version 7.1.0} benchmark~\cite{tptp} follows.
Vampire first ran to establish baseline performance in its competition \emph{CASC mode} on all problems in TPTP, with a wallclock time limit of 300 seconds.
For experimental purposes, the same environment was preserved with the exception of activating the new ``shapes'' settings with a range of different shape frequencies.

@@

\clearpage
